### 2020-05-28 writeup/proof_examples.tex
sec 4
prop 4.2 pf

\begin{proof}[Proof of Proposition \ref{prop_dist_transition}]
	In the setting of Proposition \ref{prop_dist_transition}, we have $M = \Sigma_1^{1/2}\Sigma_2^{-1/2} = \id$. Then solving equations \eqref{eq_a2} and \eqref{eq_a3} with $\hat \lambda_i=1$, we get that
	\begin{align}
		 a_1 = \frac{\rho_1(\rho_1 + \rho_2 - 1)}{(\rho_1 + \rho_2)^2} ,\quad
		& a_2 = \frac{\rho_2(\rho_1 + \rho_2 - 1)}{(\rho_1 + \rho_2)^2} , \label{simplesovlea12}\\
		 a_3 = \frac{\rho_2}{(\rho_1 + \rho_2)(\rho_1 + \rho_2 - 1)}, \quad
		& a_4 = \frac{\rho_1}{(\rho_1 + \rho_2)(\rho_1 + \rho_2 - 1)}.\label{simplesovlea34}
	\end{align}
	Using Lemma \ref{lem_minv} and Lemma \ref{lem_cov_shift}, we can track the reduction of variance from $\hat{\beta}_t^{\MTL}$ to $\hat{\beta}_t^{\STL}$ as 
\be\label{Deltavar}
\begin{split}
\delta_{\vari}&:=\sigma^2  \bigtr{(X_2^{\top}X_2)^{-1} }  - (1+\OO(n^{-\e}))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} } \\
&=\Delta_{\vari}\cdot (1+\OO(n^{-\e})) 
\end{split}
\ee
with high probability, where 
	\begin{align*}
		\Delta_{\vari} &\define \sigma^2 \bigbrace{\frac{1}{\rho_2 - 1} - \frac{1}{\rho_1 + \rho_2}\cdot\frac{1}{a_1+ a_2} } =\sigma^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)}.
	\end{align*}
	%where we use equation \eqref{eq_a12} and Lemma \ref{lem_hat_v}.
	Next for the model shift bias
	$$\delta_\beta:=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right], $$
	we can get from Lemma \ref{prop_model_shift_tight} (or rather the proof of Lemma \ref{prop_model_shift_tight}) that
\be\label{Deltabeta} 
\al_-^2(\rho_1) - \oo(1)  \le \frac{\delta_\beta}{ \Delta_{\beta}} \le \al_+^2(\rho_1) +  \oo(1) , \ee
	where 
	$$\Delta_{\beta}:=pd^2 \cdot \frac{\rho_1^2}{(\rho_1+\rho_2)^2} \cdot \frac{1 + a_3 + a_4}{(a_1 + a_2)^2}= pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}.$$	
%\begin{align*}
%		\Delta_{\beta} &\define \hat{v}^2 \bignorm{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \hat{v}\beta_t)}^2 \\
%		&= d^2 \cdot \bignormFro{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1}^2 + \bigo{p^{-1/2 + \varepsilon}d^2}
%	\end{align*}
%	Using Lemma \ref{prop_model_shift_tight}, we get an upper and lower bound on $\Delta_{\beta}$ as
%	\be\label{Deltabeta} \bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4 \le \Delta_{\beta} / \bigbrace{p\cdot d^2 \cdot \frac{c_1^2}{(c_1+c_2)^2} \cdot \frac{1 + a_3 + a_4}{(a_1 + a_2)^2} + \bigo{p^{1/2+\e}d^2} } \le \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4. \ee	
%	Hence we obtain that
%	\begin{align*}
%		\frac{1 + a_3 + a_4}{(a_1 + a_2)^2}
%		= \frac{(c_1 + c_2)^3}{(c_1 + c_2 - 1)^3} + \bigo{p^{-1/2+\varepsilon}}.
%	\end{align*}
With \eqref{Deltavar} and \eqref{Deltabeta}, we conclude that if
\be\label{upper101}pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \cdot \left( \al_+^2(\rho_1) +  \oo(1) \right) < \sigma^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)},\ee
	we have that $\delta_{\vari} > \delta_{\beta}$, which implies that $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$. We can simplify \eqref{upper101} to
	\[   d^2  < \frac{\sigma^2}{p}\frac{(\rho_1 + \rho_2 - 1)^2}{\rho_1(\rho_1 + \rho_2) (\rho_2 - 1)} \cdot \left(\bigbrace{1 + \sqrt{\frac 1 {\rho_1}}}^{-4} - \oo(1)\right), \]
Plugging into $\rho_1>40$, we obtain the first statement of Proposition \ref{prop_dist_transition}.

On the other hand, if
\be\label{upper102}pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \cdot \left( \al_-^2(\rho_1) -  \oo(1) \right) > \sigma^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)},\ee
	we have that $\delta_{\vari} < \delta_{\beta}$, which implies that $\te(\hat{\beta}_t^{\MTL})$ is larger than $\te(\hat{\beta}_t^{\STL})$. We can simplify \eqref{upper102} to
	\[   d^2  > \frac{\sigma^2}{p}\frac{(\rho_1 + \rho_2 - 1)^2}{\rho_1(\rho_1 + \rho_2) (\rho_2 - 1)} \cdot \left(\bigbrace{1 - \sqrt{\frac 1 {\rho_1}}}^{-4} +\oo(1)\right), \]
Plugging into $\rho_1>40$, we obtain the second statement of Proposition \ref{prop_dist_transition}.
\end{proof}

@@

\begin{proof}[Proof of Proposition \ref{prop_data_size}]
Recall that under the setting of Example \ref{ex_basic}, \eqref{Deltavar} and \eqref{Deltabeta} hold.  Then we get that $\te(\hat{\beta}_t^{\MTL})< \te(\hat{\beta}_t^{\STL})$ whp if
\be\label{pos1}\left(pd^2 \frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2} + \bigo{p^{1/2+\e}d^2} \right)\bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4 <  \sigma^2 \bigbrace{1 + \bigo{p^{-1/2 + \varepsilon}}};\ee
otherwise if
\be\label{neg1}\left(pd^2 \frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2} + \bigo{p^{1/2+\e}d^2} \right)\bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4 >  \sigma^2 \bigbrace{1 + \bigo{p^{-1/2 + \varepsilon}}},\ee
then we have $\te(\hat{\beta}_t^{\MTL})> \te(\hat{\beta}_t^{\STL})$ whp.

Now we prove the first statement of Proposition \ref{prop_data_size}. Notice that the function
$$ \frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2} =(c_2-1) \left(1 +\frac{c_2-2}{c_1}+\frac{1}{c_1(c_1+c_2)}\right)^{-1} $$
is strictly increasing with respect to $c_1$ as long as $c_2\ge 3$. In particular, by taking $c_1\to \infty$, we get the bound:
$$\frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2} \cdot \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4 <  (c_2-1) \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4.$$
 Hence we conclude that $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ whp as long as 
 $$pd^2 +\oo(1) \le \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^{-4}\frac{\sigma^2}{c_2-1} .$$ 
 This gives the first statement by taking $c_1 > a$.

The second statement can be proved in a similar way. Suppose $c_1 > a$ and 
$pd^2 > (1 - a^{-1/2})^{-4}\frac{\sigma^2}{c_2-1}$. If $c_1 > \frac{(c_2-2) \sigma^2}{(1-a^{-1/2})^4(1-(a+c_2-2)^{-2})(c_2 - 1) pd^2 - \sigma^2}$, we have
\begin{align*}
 & pd^2 \cdot \frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2}  \cdot \bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4  \\
 &>  \bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4 \left( 1-\frac{1}{(c_1+c_2-2)^2}\right)\cdot \frac{ pd^2(c_2-1) c_1 }{c_1+(c_2-2)}  >\sigma^2\cdot (1+\oo(1)) , 
 \end{align*}
 where in the first step we used that 
 $$ \frac{(c_1+c_2)(c_1+c_2-2)}{(c_1+c_2-1)^2}   > 1-\frac{1}{(c_1+c_2-2)^2}.$$
This shows that \eqref{neg1} holds as long as $p$ is large enough, and hence $\te(\hat{\beta}_t^{\MTL})> \te(\hat{\beta}_t^{\STL})$ holds. On the other hand, if $c_1 < \frac{(c_2-2)\sigma^2}{(1+a^{-1/2})^4(c_2 - 1) pd^2 - \sigma^2}$, then we have 
 \begin{align*}
 pd^2 \cdot \frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2}  \cdot \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4 < \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4 \cdot \frac{pd^2(c_2-1) c_1 }{c_1+(c_2-2)}  < \sigma^2\cdot (1-\oo(1)).
 \end{align*}
 This shows that \eqref{pos1} holds as long as $p$ is large enough, and hence $\te(\hat{\beta}_t^{\MTL})< \te(\hat{\beta}_t^{\STL})$ holds.
 \end{proof}

\begin{proof}[Proof of Proposition \ref{prop_covariate}]
Let 
$$M_0:=\argmin_{M\in \cal S_{\mu}}(\te(\hat{\beta}_t^{\MTL}))(M).$$ 
We now calculate $(\te(\hat{\beta}_t^{\MTL}))(M_0)$. In this case, as in Lemma \ref{lem_hat_v} we also have that 
\be\label{hatvM}|\hat v-1|=\OO(p^{-1}) \ee 
in the setting Proposition \ref{prop_covariate}. In fact, Lemma \ref{lem_hat_v} was proved assuming that $M=\id$, but its proof can be easily extended to the case with general $M\in \cal S_{\mu}$ by using that $\lambda(M)\in [\mu_{\min},\mu_{\max}]$. We omit the details here.

>>>>

\begin{proof}[Proof of Proposition \ref{prop_dist_transition}]
	In the setting of Proposition \ref{prop_dist_transition}, we have $M = \Sigma_1^{1/2}\Sigma_2^{-1/2} = \id$. Then solving equations \eqref{eq_a2} and \eqref{eq_a3} with $\hat \lambda_i=1$, we get that
	\begin{align}
		 a_1 = \frac{\rho_1(\rho_1 + \rho_2 - 1)}{(\rho_1 + \rho_2)^2} ,\quad
		& a_2 = \frac{\rho_2(\rho_1 + \rho_2 - 1)}{(\rho_1 + \rho_2)^2} , \label{simplesovlea12}\\
		 a_3 = \frac{\rho_2}{(\rho_1 + \rho_2)(\rho_1 + \rho_2 - 1)}, \quad
		& a_4 = \frac{\rho_1}{(\rho_1 + \rho_2)(\rho_1 + \rho_2 - 1)}.\label{simplesovlea34}
	\end{align}
	Using Lemma \ref{lem_minv} and Lemma \ref{lem_cov_shift}, we can track the reduction of variance from $\hat{\beta}_t^{\MTL}$ to $\hat{\beta}_t^{\STL}$ as 
\be\label{Deltavar}
\begin{split}
\delta_{\vari}&:=\sigma^2  \bigtr{(X_2^{\top}X_2)^{-1} }  - (1+\OO(n^{-\e}))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} } \\
&=\Delta_{\vari}\cdot (1+\OO(n^{-\e})) 
\end{split}
\ee
with high probability, where 
	\begin{align*}
		\Delta_{\vari} &\define \sigma^2 \bigbrace{\frac{1}{\rho_2 - 1} - \frac{1}{\rho_1 + \rho_2}\cdot\frac{1}{a_1+ a_2} } =\sigma^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)}.
	\end{align*}
	%where we use equation \eqref{eq_a12} and Lemma \ref{lem_hat_v}.
	Next for the model shift bias
	$$\delta_\beta:=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right], $$
	we can get from Lemma \ref{prop_model_shift_tight} (or rather the proof of Lemma \ref{prop_model_shift_tight}) that
\be\label{Deltabeta} 
\al_-^2(\rho_1) - \oo(1)  \le \frac{\delta_\beta}{ \Delta_{\beta}} \le \al_+^2(\rho_1) +  \oo(1) , \ee
	where 
	$$\Delta_{\beta}:=pd^2 \cdot \frac{\rho_1^2}{(\rho_1+\rho_2)^2} \cdot \frac{1 + a_3 + a_4}{(a_1 + a_2)^2}= pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}.$$	
%\begin{align*}
%		\Delta_{\beta} &\define \hat{v}^2 \bignorm{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \hat{v}\beta_t)}^2 \\
%		&= d^2 \cdot \bignormFro{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1}^2 + \bigo{p^{-1/2 + \varepsilon}d^2}
%	\end{align*}
%	Using Lemma \ref{prop_model_shift_tight}, we get an upper and lower bound on $\Delta_{\beta}$ as
%	\be\label{Deltabeta} \bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4 \le \Delta_{\beta} / \bigbrace{p\cdot d^2 \cdot \frac{c_1^2}{(c_1+c_2)^2} \cdot \frac{1 + a_3 + a_4}{(a_1 + a_2)^2} + \bigo{p^{1/2+\e}d^2} } \le \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4. \ee	
%	Hence we obtain that
%	\begin{align*}
%		\frac{1 + a_3 + a_4}{(a_1 + a_2)^2}
%		= \frac{(c_1 + c_2)^3}{(c_1 + c_2 - 1)^3} + \bigo{p^{-1/2+\varepsilon}}.
%	\end{align*}
Note that 
 \be\label{var-beta}\te(\hat{\beta}_t^{\STL})-\te(\hat{\beta}_t^{\MTL}) =\delta_{\vari} - \delta_\beta .\ee
Then we can track its sign using \eqref{Deltavar} and \eqref{Deltabeta}.

\noindent{\bf Positive transfer.} With \eqref{Deltavar} and \eqref{Deltabeta}, we conclude that if
\be\label{upper101}pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \cdot \left( \al_+^2(\rho_1) +  \oo(1) \right) < \sigma^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)},\ee
	we have that $\delta_{\vari} > \delta_{\beta}$, which implies that $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$. We can simplify \eqref{upper101} to
	\[   pd^2  <  \sigma^2 \Phi(\rho_1, \rho_2)\cdot \left(\bigbrace{1 + \sqrt{\frac 1 {\rho_1}}}^{-4} - \oo(1)\right), \]
Plugging into $\rho_1>40$, we obtain the first statement of Proposition \ref{prop_dist_transition}.

\noindent{\bf Negative transfer.} On the other hand, if
\be\label{upper102}pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \cdot \left( \al_-^2(\rho_1) -  \oo(1) \right) > \sigma^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)},\ee
	we have that $\delta_{\vari} < \delta_{\beta}$, which implies that $\te(\hat{\beta}_t^{\MTL})$ is larger than $\te(\hat{\beta}_t^{\STL})$. We can simplify \eqref{upper102} to
	\[  p d^2  >  \sigma^2 \Phi(\rho_1, \rho_2) \cdot \left(\bigbrace{1 - \sqrt{\frac 1 {\rho_1}}}^{-4} +\oo(1)\right), \]
Plugging into $\rho_1>40$, we obtain the second statement of Proposition \ref{prop_dist_transition}.
\end{proof}

@@

\begin{proof}[Proof of Proposition \ref{prop_data_size}]
Following the above proof of Proposition \ref{prop_dist_transition}, we get from \eqref{upper101} that $\te(\hat{\beta}_t^{\MTL})< \te(\hat{\beta}_t^{\STL})$ whp if
\be\label{pos1}
pd^2  \cdot \frac{\rho_1 (\rho_1 + \rho_2) (\rho_2 - 1)}{(\rho_1 + \rho_2 - 1)^2}\bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^4 <  \sigma^2  \bigbrace{1 - \oo(1)},\ee
and we get from \eqref{upper102} that $\te(\hat{\beta}_t^{\MTL})>\te(\hat{\beta}_t^{\STL})$ whp if
\be\label{neg1}pd^2  \cdot \frac{\rho_1 (\rho_1 + \rho_2) (\rho_2 - 1)}{(\rho_1 + \rho_2 - 1)^2}\bigbrace{1 - \sqrt{\frac{1}{\rho_1}}}^4 >  \sigma^2  \bigbrace{1 + \oo(1)}.\ee
%then we have $\te(\hat{\beta}_t^{\MTL})> \te(\hat{\beta}_t^{\STL})$ whp.

For the first statement of Proposition \ref{prop_data_size}, we notice that the function
$$\frac1{ \Phi(\rho_1, \rho_2)}=\frac{\rho_1 (\rho_1 + \rho_2) (\rho_2 - 1)}{(\rho_1 + \rho_2 - 1)^2}=(\rho_2-1) \left(1 +\frac{\rho_2-2}{\rho_1}+\frac{1}{\rho_1(\rho_1+\rho_2)}\right)^{-1} $$
is strictly increasing with respect to $\rho_1$ as long as $\rho_2> 2$. In particular, by taking $\rho_1\to \infty$, we get the bound:
$$\frac{\rho_1(\rho_1+\rho_2)(\rho_2-1)}{(\rho_1+\rho_2-1)^2} \cdot \bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^4 <  (\rho_2-1) \bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^4.$$
Hence as long as we take 
 $$pd^2  \le \bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^{-4}\frac{\sigma^2}{\rho_2-1}\left(1 -\oo(1)\right),$$ 
 then \eqref{pos1} holds, which shows that  $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ holds whp. Plugging into $\rho_1>50$, we obtain the first statement.

The two bounds in the second statement follows directly from \eqref{pos1} and \eqref{neg1}. We will use the following trivial inequalities 
\be\label{trivialphi}
\frac{(\rho_2-1) \rho_1 }{\rho_1+\rho_2-2}\cdot \left( 1-\frac{1}{(\rho_1+\rho_2-2)^2}\right) \le \frac{\rho_1 (\rho_1 + \rho_2) (\rho_2 - 1)}{(\rho_1 + \rho_2 - 1)^2} \le  \frac{(\rho_2-1) \rho_1 }{\rho_1+\rho_2-2}.
\ee

%This shows that \eqref{neg1} holds as long as $p$ is large enough, and hence $\te(\hat{\beta}_t^{\MTL})> \te(\hat{\beta}_t^{\STL})$ holds. 
%
%If $c_1 > \frac{(c_2-2) \sigma^2}{(1-a^{-1/2})^4(1-(a+c_2-2)^{-2})(c_2 - 1) pd^2 - \sigma^2}$, we have
%Suppose that
%$$pd^2 > (1 - a^{-1/2})^{-4}\frac{\sigma^2}{c_2-1}.$$

\noindent{\bf Positive transfer.} With \eqref{trivialphi}, we see that \eqref{pos1} is implied by the following inequality
\begin{align}\label{pos1solv}
 & pd^2 \cdot \frac{(\rho_2-1) \rho_1 }{\rho_1+\rho_2-2} \bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^4 <\sigma^2\cdot (1-\oo(1)) .
 \end{align}
 then we can solve \eqref{pos1solv} to get
 $$\rho_1 < \frac{(\rho_2-2) \sigma^2}{pd^2 \cdot (1+\rho_1^{-1/2})^4 (\rho_2 - 1)\cdot (1+\oo(1))  - \sigma^2}  .$$
 %$$\rho_1 > \frac{(\rho_2-2) \sigma^2}{(1 - {\rho_1}^{-0.5})^4 (\rho_2 - 3) pd^2 - \sigma^2}$$
 Plugging into $\rho_1>40$ and $\rho_2>500$, we conclude the upper bound for $\rho_1$ in order for positive transfer to hold.

%On the other hand, if $c_1 < \frac{(c_2-2)\sigma^2}{(1+a^{-1/2})^4(c_2 - 1) pd^2 - \sigma^2}$, then we have 
% \begin{align*}
% pd^2 \cdot \frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2}  \cdot \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4 < \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4 \cdot \frac{pd^2(c_2-1) c_1 }{c_1+(c_2-2)}  < \sigma^2\cdot (1-\oo(1)).
% \end{align*}
% This shows that \eqref{pos1} holds as long as $p$ is large enough, and hence $\te(\hat{\beta}_t^{\MTL})< \te(\hat{\beta}_t^{\STL})$ holds.

 \noindent{\bf Negative transfer.} 
With \eqref{trivialphi}, we see that \eqref{neg1} is implied by the following inequality
\begin{align}\label{neg1solv}
 & pd^2 \cdot \frac{(\rho_2-1) \rho_1 }{\rho_1+\rho_2-2}\left( 1-\frac{1}{(\rho_1+\rho_2-2)^2}\right) \bigbrace{1 - \sqrt{\frac{1}{\rho_1}}}^4 >\sigma^2\cdot (1+\oo(1)) .
 \end{align}
If the following relation holds,
$$pd^2 \cdot (1-\rho_1^{-1/2})^4(1-(\rho_1+\rho_2-2)^{-2})(\rho_2 - 1) >  \sigma^2\cdot (1+\oo(1))  , $$
 then we can solve \eqref{neg1solv} to get
 $$\rho_1 > \frac{(\rho_2-2) \sigma^2}{pd^2 \cdot (1-\rho_1^{-1/2})^4(1-(\rho_1+\rho_2-2)^{-2})(\rho_2 - 1)\cdot (1-\oo(1))  - \sigma^2}  ,$$
 %$$\rho_1 > \frac{(\rho_2-2) \sigma^2}{(1 - {\rho_1}^{-0.5})^4 (\rho_2 - 3) pd^2 - \sigma^2}$$
 Plugging into $\rho_1>40$ and $\rho_2>500$, we conclude the lower bound for $\rho_1$ in order for negative transfer to hold.
 \end{proof}

 Finally, we prove Proposition \ref{prop_covariate}, which shows that $\te(\hat{\beta}^{\MTL})$ is minimized approximately when $M$ is a scalar matrix if there are sufficiently many source datas.

\begin{proof}[Proof of Proposition \ref{prop_covariate}]
........ Let 
$$M_0:=\argmin_{M\in \cal S_{\mu}}(\te(\hat{\beta}_t^{\MTL}))(M).$$ 
We now calculate $(\te(\hat{\beta}_t^{\MTL}))(M_0)$. In this case, as in Lemma \ref{lem_hat_v} we also have that 
\be\label{hatvM}|\hat v-1|=\OO(p^{-1}) \ee 
in the setting Proposition \ref{prop_covariate}. In fact, Lemma \ref{lem_hat_v} was proved assuming that $M=\id$, but its proof can be easily extended to the case with general $M\in \cal S_{\mu}$ by using that $\lambda(M)\in [\mu_{\min},\mu_{\max}]$. We omit the details here.
